Data Preparation

### 2019-01-09 Data Preparation.Rmd

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

# Variable Engineering
We create a dataframe from the Corpus:
```{r}

>>>>

## Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data

### Transcripts

# Variable Engineering

##Course Manual 
We create a dataframe from the Corpus:
```{r}
